### 2021-09-07 img/mpcState10.tex
tex plot

\addplot [color=mycolor1, only marks, mark=triangle*, mark options={solid, fill=mycolor1, mycolor1}]
  table[row sep=crcr]{%
1	18.3\\
};
\addlegendentry{State}

\addplot [color=white!50!mycolor1, line width=1.0pt, only marks, mark=triangle, mark options={solid, white!50!mycolor1}]
  table[row sep=crcr]{%
2	19.1809073117312\\
3	19.591726028418\\
4	19.7017653509018\\
5	19.6096822707726\\
6	19.2336793296855\\
};
\addlegendentry{Prediction}

\addplot[area legend, draw=none, fill=mycolor1, fill opacity=0.1, forget plot]
table[row sep=crcr] {%
x	y\\
2	18\\
2	22\\
6	22\\
6	18\\
}--cycle;
\end{axis}
\end{tikzpicture}%

>>>>

\addplot [color=mycolor1, only marks, mark=triangle*, mark options={solid, fill=mycolor1, mycolor1}]
  table[row sep=crcr]{%
1	18.3\\
2	19.2922432972485\\
3	19.7421558473231\\
4	19.9080020336521\\
5	19.9691994260194\\
6	19.991835840366\\
7	20.6315685911097\\
8	20.8673492565163\\
9	20.9543208818143\\
10	20.9864637751245\\
};
\addlegendentry{State}

\addplot [color=white!50!mycolor1, line width=1.0pt, only marks, mark=triangle, mark options={solid, white!50!mycolor1}]
  table[row sep=crcr]{%
11	20.9349764035864\\
12	20.8913786496969\\
13	20.8170082544264\\
14	20.6458633361213\\
15	20.225626806513\\
};
\addlegendentry{Prediction}

\addplot[area legend, draw=none, fill=mycolor1, fill opacity=0.1, forget plot]
table[row sep=crcr] {%
x	y\\
11	18\\
11	22\\
15	22\\
15	18\\
}--cycle;
\end{axis}
\end{tikzpicture}%

### 2021-09-07 img/mpcState2.tex
tex plot

\addplot [color=mycolor1, only marks, mark=triangle*, mark options={solid, fill=mycolor1, mycolor1}]
  table[row sep=crcr]{%
1	18.3\\
2	19.2922432972485\\
3	19.7421558473231\\
4	19.9080020336521\\
5	19.9691994260194\\
6	19.991835840366\\
7	20.6315685911097\\
8	20.8673492565163\\
9	20.9543208818143\\
10	20.9864637751245\\
};
\addlegendentry{State}

\addplot [color=white!50!mycolor1, line width=1.0pt, only marks, mark=triangle, mark options={solid, white!50!mycolor1}]
  table[row sep=crcr]{%
11	20.9349764035864\\
12	20.8913786496969\\
13	20.8170082544264\\
14	20.6458633361213\\
15	20.225626806513\\
};
\addlegendentry{Prediction}

\addplot[area legend, draw=none, fill=mycolor1, fill opacity=0.1, forget plot]
table[row sep=crcr] {%
x	y\\
11	18\\
11	22\\
15	22\\
15	18\\
}--cycle;
\end{axis}
\end{tikzpicture}%

>>>>

\addplot [color=mycolor1, only marks, mark=triangle*, mark options={solid, fill=mycolor1, mycolor1}]
  table[row sep=crcr]{%
1	18.3\\
2	19.2922432972485\\
};
\addlegendentry{State}

\addplot [color=white!50!mycolor1, line width=1.0pt, only marks, mark=triangle, mark options={solid, white!50!mycolor1}]
  table[row sep=crcr]{%
3	19.6586714912936\\
4	19.7837827178459\\
5	19.7795571241486\\
6	19.6425574643411\\
7	19.250864938813\\
};
\addlegendentry{Prediction}

\addplot[area legend, draw=none, fill=mycolor1, fill opacity=0.1, forget plot]
table[row sep=crcr] {%
x	y\\
3	18\\
3	22\\
7	22\\
7	18\\
}--cycle;
\end{axis}
\end{tikzpicture}%

### 2021-09-07 img/mpcState3.tex
tex plot

\addplot [color=mycolor1, only marks, mark=triangle*, mark options={solid, fill=mycolor1, mycolor1}]
  table[row sep=crcr]{%
1	18.3\\
2	19.2922432972485\\
};
\addlegendentry{State}

\addplot [color=white!50!mycolor1, line width=1.0pt, only marks, mark=triangle, mark options={solid, white!50!mycolor1}]
  table[row sep=crcr]{%
3	19.6586714912936\\
4	19.7837827178459\\
5	19.7795571241486\\
6	19.6425574643411\\
7	19.250864938813\\
};
\addlegendentry{Prediction}

\addplot[area legend, draw=none, fill=mycolor1, fill opacity=0.1, forget plot]
table[row sep=crcr] {%
x	y\\
3	18\\
3	22\\
7	22\\
7	18\\
}--cycle;
\end{axis}
\end{tikzpicture}%

>>>>

\addplot [color=mycolor1, only marks, mark=triangle*, mark options={solid, fill=mycolor1, mycolor1}]
  table[row sep=crcr]{%
1	18.3\\
2	19.2922432972485\\
3	19.7421558473231\\
};
\addlegendentry{State}

\addplot [color=white!50!mycolor1, line width=1.0pt, only marks, mark=triangle, mark options={solid, white!50!mycolor1}]
  table[row sep=crcr]{%
4	19.8393846180052\\
5	19.8565364414247\\
6	19.8091433705635\\
7	19.6552196518173\\
8	19.2577473135317\\
};
\addlegendentry{Prediction}

\addplot[area legend, draw=none, fill=mycolor1, fill opacity=0.1, forget plot]
table[row sep=crcr] {%
x	y\\
4	18\\
4	22\\
8	22\\
8	18\\
}--cycle;
\end{axis}
\end{tikzpicture}%

### 2021-09-07 img/mpcState4.tex
tex plot

\addplot [color=mycolor1, only marks, mark=triangle*, mark options={solid, fill=mycolor1, mycolor1}]
  table[row sep=crcr]{%
1	18.3\\
2	19.2922432972485\\
3	19.7421558473231\\
};
\addlegendentry{State}

\addplot [color=white!50!mycolor1, line width=1.0pt, only marks, mark=triangle, mark options={solid, white!50!mycolor1}]
  table[row sep=crcr]{%
4	19.8393846180052\\
5	19.8565364414247\\
6	19.8091433705635\\
7	19.6552196518173\\
8	19.2577473135317\\
};
\addlegendentry{Prediction}

\addplot[area legend, draw=none, fill=mycolor1, fill opacity=0.1, forget plot]
table[row sep=crcr] {%
x	y\\
4	18\\
4	22\\
8	22\\
8	18\\
}--cycle;
\end{axis}
\end{tikzpicture}%

>>>>

\addplot [color=mycolor1, only marks, mark=triangle*, mark options={solid, fill=mycolor1, mycolor1}]
  table[row sep=crcr]{%
1	18.3\\
2	19.2922432972485\\
3	19.7421558473231\\
4	19.9080020336521\\
};
\addlegendentry{State}

\addplot [color=white!50!mycolor1, line width=1.0pt, only marks, mark=triangle, mark options={solid, white!50!mycolor1}]
  table[row sep=crcr]{%
5	19.9061064592983\\
6	19.8834999029294\\
7	19.8202183303531\\
8	19.6601073221883\\
9	19.2606457774807\\
};
\addlegendentry{Prediction}

\addplot[area legend, draw=none, fill=mycolor1, fill opacity=0.1, forget plot]
table[row sep=crcr] {%
x	y\\
5	18\\
5	22\\
9	22\\
9	18\\
}--cycle;
\end{axis}
\end{tikzpicture}%

### 2021-09-07 img/mpcState5.tex
tex plot

\addplot [color=mycolor1, only marks, mark=triangle*, mark options={solid, fill=mycolor1, mycolor1}]
  table[row sep=crcr]{%
1	18.3\\
2	19.2922432972485\\
3	19.7421558473231\\
4	19.9080020336521\\
};
\addlegendentry{State}

\addplot [color=white!50!mycolor1, line width=1.0pt, only marks, mark=triangle, mark options={solid, white!50!mycolor1}]
  table[row sep=crcr]{%
5	19.9061064592983\\
6	19.8834999029294\\
7	19.8202183303531\\
8	19.6601073221883\\
9	19.2606457774807\\
};
\addlegendentry{Prediction}

\addplot[area legend, draw=none, fill=mycolor1, fill opacity=0.1, forget plot]
table[row sep=crcr] {%
x	y\\
5	18\\
5	22\\
9	22\\
9	18\\
}--cycle;
\end{axis}
\end{tikzpicture}%

>>>>

\addplot [color=mycolor1, only marks, mark=triangle*, mark options={solid, fill=mycolor1, mycolor1}]
  table[row sep=crcr]{%
1	18.3\\
2	19.2922432972485\\
3	19.7421558473231\\
4	19.9080020336521\\
5	19.9691994260194\\
};
\addlegendentry{State}

\addplot [color=white!50!mycolor1, line width=1.0pt, only marks, mark=triangle, mark options={solid, white!50!mycolor1}]
  table[row sep=crcr]{%
6	19.930819433945\\
7	19.8935742358252\\
8	19.8244502967148\\
9	19.6621002443578\\
10	19.2620262577271\\
};
\addlegendentry{Prediction}

\addplot[area legend, draw=none, fill=mycolor1, fill opacity=0.1, forget plot]
table[row sep=crcr] {%
x	y\\
6	18\\
6	22\\
10	22\\
10	18\\
}--cycle;
\end{axis}
\end{tikzpicture}%

### 2021-09-07 img/mpcState6.tex
tex plot

\addplot [color=mycolor1, only marks, mark=triangle*, mark options={solid, fill=mycolor1, mycolor1}]
  table[row sep=crcr]{%
1	18.3\\
2	19.2922432972485\\
3	19.7421558473231\\
4	19.9080020336521\\
5	19.9691994260194\\
};
\addlegendentry{State}

\addplot [color=white!50!mycolor1, line width=1.0pt, only marks, mark=triangle, mark options={solid, white!50!mycolor1}]
  table[row sep=crcr]{%
6	19.930819433945\\
7	19.8935742358252\\
8	19.8244502967148\\
9	19.6621002443578\\
10	19.2620262577271\\
};
\addlegendentry{Prediction}

\addplot[area legend, draw=none, fill=mycolor1, fill opacity=0.1, forget plot]
table[row sep=crcr] {%
x	y\\
6	18\\
6	22\\
10	22\\
10	18\\
}--cycle;
\end{axis}
\end{tikzpicture}%

>>>>

\addplot [color=mycolor1, only marks, mark=triangle*, mark options={solid, fill=mycolor1, mycolor1}]
  table[row sep=crcr]{%
1	18.3\\
2	19.2922432972485\\
3	19.7421558473231\\
4	19.9080020336521\\
5	19.9691994260194\\
6	19.991835840366\\
};
\addlegendentry{State}

\addplot [color=white!50!mycolor1, line width=1.0pt, only marks, mark=triangle, mark options={solid, white!50!mycolor1}]
  table[row sep=crcr]{%
7	20.5351500004865\\
8	20.7301076659588\\
9	20.7510970131778\\
10	20.6172133181397\\
11	20.2093321462984\\
};
\addlegendentry{Prediction}

\addplot[area legend, draw=none, fill=mycolor1, fill opacity=0.1, forget plot]
table[row sep=crcr] {%
x	y\\
7	18\\
7	22\\
11	22\\
11	18\\
}--cycle;
\end{axis}
\end{tikzpicture}%

### 2021-09-07 img/mpcState7.tex
tex plot

\addplot [color=mycolor1, only marks, mark=triangle*, mark options={solid, fill=mycolor1, mycolor1}]
  table[row sep=crcr]{%
1	18.3\\
2	19.2922432972485\\
3	19.7421558473231\\
4	19.9080020336521\\
5	19.9691994260194\\
6	19.991835840366\\
};
\addlegendentry{State}

\addplot [color=white!50!mycolor1, line width=1.0pt, only marks, mark=triangle, mark options={solid, white!50!mycolor1}]
  table[row sep=crcr]{%
7	20.5351500004865\\
8	20.7301076659588\\
9	20.7510970131778\\
10	20.6172133181397\\
11	20.2093321462984\\
};
\addlegendentry{Prediction}

\addplot[area legend, draw=none, fill=mycolor1, fill opacity=0.1, forget plot]
table[row sep=crcr] {%
x	y\\
7	18\\
7	22\\
11	22\\
11	18\\
}--cycle;
\end{axis}
\end{tikzpicture}%

>>>>

\addplot [color=mycolor1, only marks, mark=triangle*, mark options={solid, fill=mycolor1, mycolor1}]
  table[row sep=crcr]{%
1	18.3\\
2	19.2922432972485\\
3	19.7421558473231\\
4	19.9080020336521\\
5	19.9691994260194\\
6	19.991835840366\\
7	20.6315685911097\\
};
\addlegendentry{State}

\addplot [color=white!50!mycolor1, line width=1.0pt, only marks, mark=triangle, mark options={solid, white!50!mycolor1}]
  table[row sep=crcr]{%
8	20.7920443673713\\
9	20.8334722976929\\
10	20.7930677686674\\
11	20.6350899301155\\
12	20.2189083589457\\
};
\addlegendentry{Prediction}

\addplot[area legend, draw=none, fill=mycolor1, fill opacity=0.1, forget plot]
table[row sep=crcr] {%
x	y\\
8	18\\
8	22\\
12	22\\
12	18\\
}--cycle;
\end{axis}
\end{tikzpicture}%

### 2021-09-07 img/mpcState8.tex
tex plot

\addplot [color=mycolor1, only marks, mark=triangle*, mark options={solid, fill=mycolor1, mycolor1}]
  table[row sep=crcr]{%
1	18.3\\
2	19.2922432972485\\
3	19.7421558473231\\
4	19.9080020336521\\
5	19.9691994260194\\
6	19.991835840366\\
7	20.6315685911097\\
};
\addlegendentry{State}

\addplot [color=white!50!mycolor1, line width=1.0pt, only marks, mark=triangle, mark options={solid, white!50!mycolor1}]
  table[row sep=crcr]{%
8	20.7920443673713\\
9	20.8334722976929\\
10	20.7930677686674\\
11	20.6350899301155\\
12	20.2189083589457\\
};
\addlegendentry{Prediction}

\addplot[area legend, draw=none, fill=mycolor1, fill opacity=0.1, forget plot]
table[row sep=crcr] {%
x	y\\
8	18\\
8	22\\
12	22\\
12	18\\
}--cycle;
\end{axis}
\end{tikzpicture}%

>>>>

\addplot [color=mycolor1, only marks, mark=triangle*, mark options={solid, fill=mycolor1, mycolor1}]
  table[row sep=crcr]{%
1	18.3\\
2	19.2922432972485\\
3	19.7421558473231\\
4	19.9080020336521\\
5	19.9691994260194\\
6	19.991835840366\\
7	20.6315685911097\\
8	20.8673492565163\\
};
\addlegendentry{State}

\addplot [color=white!50!mycolor1, line width=1.0pt, only marks, mark=triangle, mark options={solid, white!50!mycolor1}]
  table[row sep=crcr]{%
9	20.8868479256373\\
10	20.8717333373315\\
11	20.8087284948109\\
12	20.6419287074761\\
13	20.2228485328721\\
};
\addlegendentry{Prediction}

\addplot[area legend, draw=none, fill=mycolor1, fill opacity=0.1, forget plot]
table[row sep=crcr] {%
x	y\\
9	18\\
9	22\\
13	22\\
13	18\\
}--cycle;
\end{axis}
\end{tikzpicture}%

### 2021-09-07 img/mpcState9.tex
tex plot

\addplot [color=mycolor1, only marks, mark=triangle*, mark options={solid, fill=mycolor1, mycolor1}]
  table[row sep=crcr]{%
1	18.3\\
2	19.2922432972485\\
3	19.7421558473231\\
4	19.9080020336521\\
5	19.9691994260194\\
6	19.991835840366\\
7	20.6315685911097\\
8	20.8673492565163\\
};
\addlegendentry{State}

\addplot [color=white!50!mycolor1, line width=1.0pt, only marks, mark=triangle, mark options={solid, white!50!mycolor1}]
  table[row sep=crcr]{%
9	20.8868479256373\\
10	20.8717333373315\\
11	20.8087284948109\\
12	20.6419287074761\\
13	20.2228485328721\\
};
\addlegendentry{Prediction}

\addplot[area legend, draw=none, fill=mycolor1, fill opacity=0.1, forget plot]
table[row sep=crcr] {%
x	y\\
9	18\\
9	22\\
13	22\\
13	18\\
}--cycle;
\end{axis}
\end{tikzpicture}%

>>>>

\addplot [color=mycolor1, only marks, mark=triangle*, mark options={solid, fill=mycolor1, mycolor1}]
  table[row sep=crcr]{%
1	18.3\\
2	19.2922432972485\\
3	19.7421558473231\\
4	19.9080020336521\\
5	19.9691994260194\\
6	19.991835840366\\
7	20.6315685911097\\
8	20.8673492565163\\
9	20.9543208818143\\
};
\addlegendentry{State}

\addplot [color=white!50!mycolor1, line width=1.0pt, only marks, mark=triangle, mark options={solid, white!50!mycolor1}]
  table[row sep=crcr]{%
10	20.9219229812564\\
11	20.8859883781932\\
12	20.8146703364917\\
13	20.6446665111643\\
14	20.2246553047596\\
};
\addlegendentry{Prediction}

\addplot[area legend, draw=none, fill=mycolor1, fill opacity=0.1, forget plot]
table[row sep=crcr] {%
x	y\\
10	18\\
10	22\\
14	22\\
14	18\\
}--cycle;
\end{axis}
\end{tikzpicture}%

### 2021-09-07 presentation/presentation.tex
tex plot

\usepackage[english]{babel}
\usepackage{tikz}
\usetikzlibrary{calc,shapes,positioning}
\usetikzlibrary{overlay-beamer-styles}
% or whatever

@@

\begin{frame}{Model Predictive Control}
  Find sequence, \pause apply first control, \pause rinse repeat \pause $\to$ Receding Horizon

  \begin{figure}
    \centering
    \foreach \i in {1,...,10}{\includegraphics<\i>[width=.5\textwidth]{mpc\i.pdf}%
    }
  \end{figure}
\end{frame}

\begin{frame}
  \begin{itemize}
    \item Problem: Complexity depends on $N_{p},m,p$ and sizes of $\vec{x}$ and $\vec{u}$
    \item Solution: Divide and Conquer
  \end{itemize}
\end{frame}

>>>>

\usepackage[english]{babel}
\usepackage{tikz}
\usetikzlibrary{calc,shapes,positioning}
\usetikzlibrary{overlay-beamer-styles}
\usepackage{pgfplots}
 \usetikzlibrary{plotmarks}
  \usetikzlibrary{arrows.meta}
  \usepgfplotslibrary{patchplots}
  \usepackage{grffile}
% or whatever

@@

\newlength\fheight
\newlength\fwidth
\setlength\fwidth{.35\textwidth}
\setlength\fheight{.8\fwidth}

\begin{frame}{Model Predictive Control}
  \only<1->{Find optimal control sequence}%
  \only<2->{, apply first element}%
  \only<3->{, rinse repeat}%
  \only<4->{ $\to$ Receding Horizon}%

  \begin{figure}
    \centering
    \foreach \i in {1,...,10}{%
      % \includegraphics<\i>[width=.5\textwidth]{mpc\i.pdf}%
      \only<{\i}>{\input{../img/mpcState\i.tex}}%
      \only<{\i}>{\input{../img/mpcControl\i.tex}}%
    }
  \end{figure}
\end{frame}

\begin{frame}[label=current]
  \begin{itemize}
    \item Problem: Complexity depends on $N_{p},m,p$ and sizes of $\vec{x}$ and $\vec{u}$
    \item Solution: Divide and Conquer
  \end{itemize}
  \vfill
  \begin{figure}
    \centering
    \only<1>{
    \begin{tikzpicture}[font=\small,thick,node distance=.6cm and 6cm]
      \node[draw,
      rectangle,
      trapezium stretches,
      align=center,
      fill=supelecRed!10,
      alt=<{3}>{fill=supelecRed!90,text=white},
      minimum width=3.5cm,
      minimum height=4cm
      ] (block1) {MPC};
    \end{tikzpicture}
    }%
    \only<2>{
      \tikzset{mpcSmall/.style={
      rectangle,
      align=center,
      fill=supelecRed!10,
      minimum width=2.cm,
      minimum height=.5cm},
    coordinator/.style={
    rectangle,
    trapezium stretches,
    align=center,
    fill=supelecRed!10,
    minimum width=1cm,
    minimum height=4cm
    }}
  \begin{tikzpicture}[font=\small,thick,node distance=.35cm and .5cm]

    \node[draw,
    mpcSmall
    ] (block1) {MPC};

    \node[draw,
    mpcSmall,
    below=of block1,
    ] (block2) {MPC};

    \node[draw,
    mpcSmall,
    below=of block2,
    ] (block3) {MPC};

    \node[draw,
    mpcSmall,
    fill=none,
    draw=white,
    below=of block3,
    ] (block4) {\vdots};
    \node[draw,
    mpcSmall,
    below=of block4,
    ] (block5) {MPC};

    \node[draw,
    coordinator,
    right=of block3,
    ] (coordinator) {\rotatebox{90}{Coordinator}};

\draw (block2) -- (coordinator);
\draw (block3) -- (coordinator);

  \end{tikzpicture}
}%

\end{figure}
\end{frame}
